Optimized Multi-Frequency Spectra for Numerical Radiative Transfer

### 2011-10-24 doc/paper/ms.tex
Added Multiplot.py, updated a few scripts to use it.

Unfortunately, the vast majority of radiative transfer simulations run to date have only considered radiation at a single frequency.  While this monochromatic approach is the natural first step computationally-speaking, sampling radiation fields at multiple frequencies is essential for accurately calculating the properties of the medium through which photons propagate.  The mere presence of ionizing photons ensures that gas surrounding a radiation source will become ionized and heated, but the degree to which gas is ionized and heated depends on the total number of ionizing photons and their spectral energy distribution (SED).  As a result, we should expect the properties of gas surrounding a blackbody source of ultraviolet (UV) photons to be quite different from those of a power-law X-ray source such as an accreting black hole, for example.  Even relatively small changes in SED can produce noticeable differences in surrounding gas properties, like changing the power-law index of a black-hole accretion spectrum (\cite{Kuhlen2005}; \cite{Thomas2008}).  But, these expectations are built on the assumption that each source is represented by a continuous SED, not one we have constructed with \nnu discrete frequency bins.  As we'll see in \S2, for a given source, the properties of the surrounding medium can be altered considerably solely due to the manner in which we discretize its spectrum.

@@

To demonstrate the functionality of the code, we repeat tests 1 and 2 from the Radiative Transfer Comparison Project (\cite{Iliev2006}; hereafter referred to as RT06).  Test 1 is the expansion of an HII region in a hydrogen-only, isothermal medium surrounding a monochromatic source of 13.6 eV photons.

\begin{figure}[htbp]
\centering
\includegraphics[scale=0.4]{figures/RT_Test1_IfrontEvolution.ps}
\vspace{-20pt}
\caption{\textit{Top:} Comparison of the calculated (dashed) and analytic (solid) positions of an expanding ionization front in a hydrogen-only, isothermal medium. \textit{Bottom:} Ratio of the calculated and analytic solutions.}
\label{fig:RT_Test1_IfrontEvolution}
%\end{center}
\end{figure}

>>>>

Unfortunately, the vast majority of radiative transfer simulations run to date have only considered radiation at a single frequency.  While this monochromatic approach is the natural first step computationally-speaking, sampling radiation fields at multiple frequencies is essential for accurately calculating the properties of the medium through which photons propagate.  The mere presence of ionizing photons ensures that gas surrounding a radiation source will become ionized and heated, but the degree to which gas is ionized and heated depends on the total number of ionizing photons and their spectral energy distribution (SED).  As a result, we should expect the properties of gas surrounding a blackbody source of ultraviolet (UV) photons to be quite different from those of a power-law X-ray source such as an accreting black hole, for example.  Holding the bolometric luminosity of an object constant, even relatively small changes in SED can produce noticeable differences in surrounding gas properties, like changing the power-law index of a black-hole accretion spectrum (\cite{Kuhlen2005}; \cite{Thomas2008}).  But, these expectations are built on the assumption that each source is represented by a continuous SED, not one we have constructed with \nnu discrete frequency bins.  As we'll see in \S2, for a given source, the properties of the surrounding medium can be altered considerably solely due to the manner in which we discretize its spectrum.

@@

To demonstrate the functionality of the code, we repeat tests 1 and 2 from the Radiative Transfer Comparison Project (\cite{Iliev2006}; hereafter referred to as RT06).  Test 1 is the expansion of an HII region in a hydrogen-only, isothermal medium surrounding a monochromatic source of 13.6 eV photons. We adopt the parameters used in \citet{Wise2011}: constant temperature $T = 10^4 \ \mathrm{K}$, hydrogen number density $n_H = 10^{-3} \ \mathrm{cm^{-3}}$, ionized fraction $x = 1.2 \times 10^-3$, in a box $L_{\mathrm{box}} = 6.6 \ \mathrm{kpc}$ in size, and with photon luminosity $\dot{Q} = 5\times10^{48} \ \mathrm{s^{-1}}$.

\begin{figure*}[htbp]
\centering
\includegraphics[scale=0.8]{figures/RT06_1_IfrontEvolution.eps}
\caption{\textit{Top:} Comparison of the numerical (dashed) and analytic (solid) solutions for the position of an expanding ionization front as a function of time in a hydrogen-only, isothermal medium (RT06 problem \# 1).  The numerical solution here was obtained using 400 grid cells. \textit{Bottom:} Ratio of the calculated and analytic solutions as a function of time and grid resolution. }
\label{fig:RT_Test1_IfrontEvolution}
\end{figure*}
